
\documentclass{letter}

\signature{Jo\~{a}o Bento}
\begin{document}
\begin{letter}{}
\opening{Dear Dr. Ireland}

I'm writing to submit my application to the Post-Doctoral position you advertised on the American Astronomical Society job register page (reference number JRID41677) on the 1st of February, 2012. I am currently a PhD student in the last stages of my degree at the University of Warwick, working on several aspects of transiting exoplanet photometry.

I am very interested in this position because I believe the research I have been conducting has given me the skills directly related with the goals of the project. Moreover, I wish to expand my knowledge into other areas of astronomy and an opportunity to work in instrumentation and implementation is very attractive.

I am an active member of the SuperWASP consortium, as well as being one of the first members to take part in the planning and developing of the Next Generation Transit Survey, soon to be commissioned at ESO's Paranal Observatory. I have also planned all aspects of data collection and subsequently carried out observations and the data analysis of planetary transits using the multi-band photometer ULTRACAM in the context of an effort to perform transmission studies of large scale height exoplanets.

The attached file contains my CV, list of publications, research statement and the contact details of three people who can provide reference letters upon request. Thank you very much for your consideration. I look forward to hearing from you. 

%\dots
\closing{Sincerely,}
%\ps{P.S. Here goes your ps.}

Department of Physics, \\University of Warwick \\ Coventry, CV4 7AL \\ United Kingdom
%\encl{Enclosures.}
\end{letter}
\end{document}
